Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-26 manuscript.Rmd
Small multiples working.

bigList <- left_join(n.so, n.yr) %>%
    group_by(title, year) %>%
    summarize(N = n())
bigList$shortTitle <- abbreviate(bigList$title)

bigList2 <- left_join(bigList, hIndex, by = "title")
bigList2 <- within(bigList2, quartile <- as.integer(cut(h5Index, quantile(h5Index, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))
table(bigList2$h5Index, useNA = "always")

bigList2$quartileFactor <- as.factor(bigList2$quartile)
bigList2 <- bigList2 %>% arrange(desc(quartileFactor))

ggplot(bigList2, aes(year, N, group = 1, colour=quartileFactor)) + geom_line() + 
    facet_wrap(~ shortTitle, ncol=7) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    scale_x_discrete(breaks=seq(1989, 2020, 8)) + 
    ylim(0, 150)

@@

@@

cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
evidence.summary <- ungroup(evidence.summary)
evidence.summary$year <- as.numeric(evidence.summary$year)
evidence.summary$studyType <- as.factor(evidence.summary$studyType)

@@

ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary)), 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.80, colour = "black", size = .2) + 
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)),
        labels = c("Systematic review", "RCT", "Quasi-experimental", 
           "Meta-analysis")) +
  ylim(c(0, 60)) + 
    scale_x_continuous(breaks = seq(0,24, 2), labels = year.labs) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1), 
          panel.grid.minor=element_blank(),
         legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("Frequency") + 
    xlab("Year") + 
    labs(fill = "Study type") + 
    scale_y_continuous(breaks = seq(0,60, 10))

@@

levels(df$studyType) <- c("Meta-analysis", "Quasi-experimental", "Observational", "RCT", "Systematic review")

ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
    group = studyType), na.rm=TRUE) + 
    geom_smooth(aes(fill=studyType)) + facet_wrap(~studyType) + 
    scale_fill_manual(values = cp) +   
    scale_color_manual(values = cp) + 
    theme(legend.position = "none") + 
    ylab("Proportion") + 
    geom_point(colour = "black", alpha = .60)

#####################

@@

j.order <- unique(df$journal[order(df$N.sort, decreasing = FALSE)]) 
df$journal <- factor(df$journal, levels = j.order)

ggplot(na.omit(df), aes(x = N, y= journal, group = journal, colour = studyType)) + 
    geom_segment(aes(yend = journal), xend=0, colour="grey50") +
    geom_point(size = 2.5) + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    facet_grid(.~studyType) + 
    theme(panel.grid.major.y = element_blank())

@@

j.order <- unique(df2$journal[order(df2$Prop, decreasing = FALSE)]) 
df2$journal <- factor(df2$journal, levels = j.order)

ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
    geom_segment(aes(yend = journal), xend=0, colour="#b2abd2") +
    geom_point(aes(size = Overall.N.Strength), colour = "#5e3c99") + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    theme(panel.grid.major.y = element_blank())

>>>>

```{r plotSmallMultiples}
hIndex.df <- arrange(hIndex, desc(h5Median)) %>% select(title, h5Median)
hIndex.df$top10 <- NA
hIndex.df$top10[1:10] <- "yes"
hIndex.df$top10[11:nrow(hIndex.df)] <- "no"
hIndex.df <- data.frame(hIndex.df)

sm.df <- left_join(n.so, n.yr) %>%
    group_by(title, year) %>%
    summarize(N = n()) %>%
    mutate(Overall.N = sum(N)) %>%
    ungroup() %>%
    arrange(desc(Overall.N), title)

sm.df <- full_join(sm.df, hIndex.df, by = "title") %>% 
    ungroup %>% 
    select(-h5Median)

sm.df$top10 <- ifelse(is.na(sm.df$top10), "no", sm.df$top10)

title <- sm.df %>% arrange(desc(Overall.N)) %>% distinct(title)

title.order <- title$title

sm.df$title2 <- factor(sm.df$title, levels = (title.order))

Overall.N <- distinct(sm.df, title)

x.df <- data.frame(title = Overall.N$title, label = title$Overall.N)

xpos = rep(10, 78)
ypos = rep(130, 78)
lab <- Overall.N$Overall.N
title2 <- unique(sm.df$title2)

ldata <- data.frame(xpos, ypos, lab, title2)

ggplot(sm.df, aes(year, N, group = 1)) + geom_line(aes(colour = top10)) + 
facet_wrap( ~ title2, ncol=7) +
theme_bw() +
theme(panel.grid.major = element_blank(), 
panel.grid.minor = element_blank(), 
axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
scale_x_discrete(breaks=seq(1989, 2020, 8)) + 
ylim(0, 150) + 
geom_text(data = ldata, aes(x =xpos, y = ypos, label = lab, size =1), parse=FALSE)

```{r plotScatter}

@@

evidence.df$studyType <- factor(evidence.df$studyType, labels= c("Meta-analysis", "Quasi-experimental", "RCT", "Systematic review"))

evidence.df$studyType <- factor(evidence.df$studyType, 
    levels(evidence.df$studyType)[c(1,4,3,2)])

@@

cp <- c("#b2abd2", "#5e3c99", "#fdb864", "#e66101" )
evidence.summary <- ungroup(evidence.summary)
evidence.summary$year <- as.numeric(evidence.summary$year)
#evidence.summary$studyType <- as.factor(evidence.summary$studyType)

@@

ggplot(as.data.frame(xtabs(N~year+studyType, evidence.summary)), 
    aes(x = as.numeric(year), y = Freq, fill=studyType)) + 
    geom_area(alpha=.60, colour = "black", size = .2) + 
    scale_fill_manual(values=cp, 
        breaks = rev(levels(evidence.summary$studyType)))+
  ylim(c(0, 60)) + 
    scale_x_continuous(breaks = seq(0,24, 2), labels = year.labs) + 
    theme(axis.text.x = element_text(angle = 45, hjust=1), 
          panel.grid.minor=element_blank(),
         legend.position=c(.25,.80),
#         legend.background = element_blank(), 
         legend.key = element_blank()   ) + 
    ylab("N") + 
    xlab("Year") + 
    labs(fill = "Study type") +
    scale_y_continuous(breaks = seq(0,90, 10))

@@

ggplot(na.omit(df), aes(year, studyProp, colour = studyType, 
    group = studyType), na.rm=TRUE) + 
    geom_smooth(aes(fill=studyType), alpha = .60, colour = "dimgray") + facet_wrap(~studyType) + 
    scale_fill_manual(values = cp) +   
    scale_color_manual(values = cp) + 
    theme(legend.position = "none") + 
    ylab("Proportion") + 
    geom_point(colour = "black", alpha = .60) + 
    annotate("segment", x = 1989, y = 0, xend = 2013, yend = 0, alpha = .6, 
        linetype= "solid") +
    annotate("segment", x = 1989, y = 0, xend = 1989, yend = .0175, alpha = .6, 
        linetype = "solid") +
    annotate("segment", x = 2013, y = 0, xend = 2013, yend = .0175, alpha = .6,
             linetype = "solid") +
    scale_x_continuous(breaks = seq(1989, 2014, 4)) + 
     theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_y_continuous(breaks = seq(0, .015, .005))

######1989########

@@

df1 <- df

#df1$studyType <- factor(df1$studyType)
j.order <- unique(df1$journal[order(df1$N.sort, decreasing = FALSE)]) 
df1$journal <- factor(df1$journal, levels = j.order)

ggplot(na.omit(df1), aes(x = N, y= journal, group = journal, colour = studyType)) + 
    geom_segment(aes(yend = journal), xend=0, colour="grey50") +
    geom_point(size = 2.5) + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    facet_grid(.~studyType) + 
    theme(panel.grid.major.y = element_blank(), legend.position = "none") + 
    xlim(0, 600) + 
    ylab("Journal") +  
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
    scale_x_continuous(breaks = seq(0, 60, 10))

@@

j.order <- unique(df2$journal[order(df2$Overall.N.Strength, decreasing = FALSE)]) 
df2$journal <- factor(df2$journal, levels = j.order)

df2  <- within(df2, quartile <- as.integer(cut(Overall.N.Strength, quantile(Overall.N.Strength, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))

ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
    geom_segment(aes(yend = journal), xend=0) +
    geom_point(aes(size = Overall.N.Strength)) + 
    theme_bw() +
    theme(panel.grid.major.y = element_blank(), legend.position = c(.62, .65)) +
    ylab("Journal") +
    xlab("Proportion") +
    labs(size = "Total number of \nEBP articles published")
